Spin canonical divisors of log stacky curves

### 2015-07-01 stacky_write_up/spin_cring.tex
indent & linebreak further research

\ssec{Bounds on Generators and Relations in High Genus}
\todo{Make edits that you want to further incorporate Reid's paper}

@@

\begin{enumerate}
	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms. As defined in Adler and Ramanan (in the passage immediately following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. Fractional modular forms also make an apperance in Milnor \cite[$\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3^{e_3} = 0$.

@@

\begin{question}
\label{ques:fractional-weight}
If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ where $K$ is the canonical divisor of $\sx$, can one bound the degrees of generators and relations of $R_D$?
\end{question}
Note that that the above question is answered affirmatively in the case that $\sx$ has genus $0$ and $D$ is effective, as follows by inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature $(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most $2e$. Additionally, it may be possible to modify the proof of Lemma ~\ref{lem:raise-stacky-order} to extend to the setting of fractional weight modular forms. Given suitable generalizations of these lemmas, one may be able to approach the problem of finding generators and relations for fractional weight modular forms using techniques similar to those in this paper.
	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense. The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner. In particular, Lemma ~\ref{lem:raise-stacky-order} constructs generators with non-maximal pole orders at certain points, making the relations non-generic. 
\begin{question}
\label{ques:generic-initial}
If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$, does there exist a function $\sigma \mapsto d(\sigma)$ so that the generic initial ideal {\rm(} with some specified ordering{\rm)} is generated in degree at most $d(\sigma)$? Can one write down the generic initial ideal explicitly?
\end{question}
	\item As noted in Remark ~\ref{rem:explicit-generators}, the proof of Theorem ~\ref{thm:main} given in this paper gives an explicit procedure for computing the generators and relations of $R_L$ when the genus of $\sx$ is $0$ or $1$.
\begin{question}
\label{ques:algorithm}
Can one give an algorithm for explicitly computing the generators and relations for an arbitrary genus $g \geq 2$ curve?
\end{question}
Suppose the generators and relations of $R_{L_X}$ are known, where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an algorithm for determining the generators of $L$. This raises the following Petri-like question:
\begin{question}
\label{ques:spin-canonical-petri}
Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical divisor $L \in \di X$, can one write down a set of minimal generators and minimal relations for $R_L$? If so, can one give the generic ideal of $R_L$ or the generic initial ideal of $R_L$, as defined in Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}?
\end{question}
In particular, if Question ~\ref{ques:spin-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
	\todo{This last one doesn't seem particularly interesting. Should we remove it?}
	\item While Theorem ~\ref{thm:main} gives a minimal set of generators for the log spin canonical ring $R_L,$ the set of relations is not minimal. In many of the $g = 0$ and $g=1$ cases, it is not too difficult to see that our inductive procedure also yields a minimal set of relations for $R_L$. One might investigate whether the generators and relations given by the inductive proof of Theorem ~\ref{thm:main} are always minimal.
\end{enumerate}

>>>>

\ssec{Bounds on Generators and Relations in High Genus}
\label{ssec:bounds-high-genus}
\todo{Make edits that you want to further incorporate Reid's paper}

@@

\begin{enumerate}
	\item One direction for further research is to 
		extend the results of this paper to divisors $D \in \di \sx$ on a 
		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
		divisors would translate to rings of fractional weight modular 
		forms. As defined in Adler and Ramanan (in the passage immediately 
		following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form 
		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
		line bundle $\eta$ so that there exists a line bundle $\gamma$ with 
		$\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^
		1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an 
		explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. 
		Fractional modular forms also make an apperance in Milnor \cite[$
		\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 
		shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e
		_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of 
		fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3
		^{e_3} = 0$.

@@

		\begin{question}
		\label{ques:fractional-weight}
			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ 
			where $K$ is the canonical divisor of $\sx$, can one bound the 
			degrees of generators and relations of $R_D$?
		\end{question}
		Note that that the above question is answered affirmatively in the 
		case that $\sx$ has genus $0$ and $D$ is effective, as follows by 
		inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature 
		$(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
		$2e$. Additionally, it may be possible to modify the proof of Lemma
		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
		weight modular forms. Given suitable generalizations of these 
		lemmas, one may be able to approach the problem of finding 
		generators and relations for fractional weight modular forms using 
		techniques similar to those in this paper.

	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky},
		the notion of a generic initial ideal is defined, which 
		encapsulates the idea of whether the relations for $R_L$ are 
		generically chosen, in a precise sense. The proof of Theorem
		~\ref{thm:main} decidedly does not yield a generic initial ideal, 
		as generators and relations are constructed in a highly nongeneric 
		manner. In particular, Lemma ~\ref{lem:raise-stacky-order} 
		constructs generators with non-maximal pole orders at certain 
		points, making the relations non-generic. 
		\begin{question}
		\label{ques:generic-initial}
			If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$,
			does there exist a function $\sigma \mapsto d(\sigma)$ so that
			the generic initial ideal {\rm(} with some specified ordering{\rm)}
			is generated in degree at most $d(\sigma)$? Can one write down the
			generic initial ideal explicitly?
		\end{question}

	\item As noted in Remark ~\ref{rem:explicit-generators}, the 
		proof of Theorem ~\ref{thm:main} given in this paper gives an 
		explicit procedure for computing the generators and relations of $R_
		L$ when the genus of $\sx$ is $0$ or $1$.
		\begin{question}
		\label{ques:algorithm}
			Can one give an algorithm for explicitly computing the generators 
			and relations for an arbitrary genus $g \geq 2$ curve?
		\end{question}
		Suppose the generators and relations of $R_{L_X}$ are known, 
		where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the 
		coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor 
		of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an 
		algorithm for determining the generators of $L$. This raises the 
		following Petri-like question:
		\begin{question}
		\label{ques:spin-canonical-petri}
			Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical 
			divisor $L \in \di X$, can one write down a set of minimal 
			generators and minimal relations for $R_L$? If so, can one give the 
			generic ideal of $R_L$ or the generic initial ideal of $R_L$, as 
			defined in Voight and Zureick Brown \cite[Definition 2.2.7]
			{vzb:stacky}?
		\end{question}
		In particular, if Question ~\ref{ques:spin-canonical-petri} were 
		answered affirmatively one would be able to write down explicit 
		generators and relations for $R_L$ on a stacky curve, essentially 
		by inductively applying Lemma ~\ref{lem:raise-stacky-order}.

	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
		the work of Reid \cite[p. 35]{reid:infinitesimal}. We use his 
		construction of a uniform bound on the generation of the half-
		canonical ring and its ideal of relations at 5 and 10 in the non-
		log, non-stacky case when genus is at least 2.  We extend this 
		bound of 5 and 10 to the log case, and then apply our inductive 
		lemmas to add stacky points and get bounds of $\max(5,e)$ and $\max(
		10, 2e)$.  Reid in fact proves something slightly stronger: that in 
		most cases his bound is actually 3 and 6 with well-characterized 
		exceptions.
		\begin{question}\label{ques:reduce-5,10-to-4,8}
			Can we reduce the bounds in Theorem \ref{thm:main} on 
			generation from $\max(5,e)$ and $\max(10, 2e)$ to $\max(4,e)$ and $
			\max(8, 2e)$. 
		\end{question}
		\begin{rem}\label{rem:reduce-3,6}
			It is unlikely that this can be reduced further, because Lemma 
			\ref{lem:sat-2}, which allows us to add a stacky point in genus $g>0
			$ saturated at 2, requires a generator in degree 4 and potentially 
			a relation in degree 8, even when inductively adding on stacky 
			points of stabilizer order 3.
			\end{rem}

	\todo{This last one doesn't seem particularly interesting. Should we remove it?}
	\item While Theorem ~\ref{thm:main} gives a minimal set of 
		generators for the log spin canonical ring $R_L,$ the set of 
		relations is not minimal. In many of the $g = 0$ and $g=1$ cases, 
		it is not too difficult to see that our inductive procedure also 
		yields a minimal set of relations for $R_L$. One might investigate 
		whether the generators and relations given by the inductive proof 
		of Theorem ~\ref{thm:main} are always minimal.
		\end{enumerate}
